---
title: "brian_evan_data"
author: "Mark Carthon"
date: "11/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set working directory and load data
```{r}
setwd("~/NYCDSA/Machine Learning Project Proposal/Machine Learning Project Proposal")
data = read.csv('brian_evan_data.csv')
```

# Load libraries
```{r}
library(glmnet)
library(MASS)
library(car)
library(dplyr)
library(jtools)
library(caret)
```

# Log GrLivArea
```{r}
data$GrLivArea    = log1p(data$GrLivArea)
```

# Preprocess data
```{r}
data = sapply(data, as.numeric)
data = as.data.frame(scale(data))
```

# Proportion of missing data by column
```{r}
sort(colMeans(is.na(data)), decreasing = T)
```


# Set parameter grid for lambda
```{r}
grid = 10^seq(from = -0.9, to = 100, length.out = 20)
```

# Form predictor and target matrices
```{r}
x = model.matrix(SalePrice ~ ., data = data)[, ! names(data) %in% c("SalePrice", "price_per_area")]
y = data$SalePrice
```

# Run that lasso boi!
```{r}
lasso.model = glmnet(x, y, alpha = 1, lambda = grid)

dim(coef(lasso.model))
coef = as.matrix(coef(lasso.model))
coef = as.data.frame(coef)

results = sort(abs(rowMeans(coef)), decreasing = TRUE)
results = results[results > 0]
results = t(results)
results = as.data.frame(results)
```

# Collect results from lasso for MLR
```{r}
lasso_features = subset(data,select = c("SalePrice"
                                        ,colnames(results)[-length(colnames(results))],
                                        "isu_dist","airport_dist","downtown_dist",
                                        "X2ndFlrSF"))
```

# Run the MLR like a boss!
```{r}
model = lm(formula = SalePrice ~ . - OverallQual,
           data = lasso_features)
summary(model)
plot(model)
vif(model)
```
# Outlier points are: 2566, 925
# Insignificant features:FireplaceQu
# Remove outliers and run LMR again to see what happens
```{r}
lasso_features = lasso_features[-c(2566,925),]
drop = c("OverallQual", "TotRmsAbvGrd", "LotArea", "GarageCars")
lasso_features = lasso_features[, !names(lasso_features) %in% drop]

model = lm(formula = SalePrice ~ .,
           data = lasso_features)
summary(model)
plot(model)
vif(model)
```

# Write lasso_features to csv
```{r}
#write.csv(lasso_features, 
  #        file = "C:\\Users\\Mark Anthony Carthon\\Documents\\NYCDSA\\Machine Learning Project Proposal\\Machine Learning Project #Proposal\\lasso_features.csv")
```

# Run train-test-split
```{r}
set.seed(0)

train = sample(x = nrow(lasso_features),
               size = 0.8 * nrow(lasso_features),
               replace = F)

test = setdiff(1:nrow(lasso_features), train)
test = sample(x = test, size = length(test), replace = F)
```

# Create matrices of predictors and labels
```{r}
#x_train = model.matrix(object = SalePrice ~ ., data = lasso_features[train,])
x_train = lasso_features[train,]
y_train = lasso_features$SalePrice[train]
#x_test  = model.matrix(object = SalePrice ~ ., data = lasso_features[test,])
x_test = lasso_features[test,]
y_test = lasso_features$SalePrice[test]
```


## Cross Validation

```{r}
set.seed(0)

train_control = trainControl(method = "repeatedcv", number  = 10, repeats = 3)

cvmodel = train(SalePrice ~ ., data = x_train, trControl = train_control, method = "lm", tol = 2e-16)

print(cvmodel)

summary(cvmodel)
```

```{r}
set.seed(0)

drop = c("FullBath", "FireplaceQu", "TotRmsAbvGrd")
lasso_features = lasso_features[, !names(lasso_features) %in% drop]

x_train = lasso_features[train,]
y_train = lasso_features$SalePrice[train]
x_test = lasso_features[test,]
y_test = lasso_features$SalePrice[test]

train_control = trainControl(method = "repeatedcv", number  = 10, repeats = 3)

cvmodel = train(SalePrice ~ ., data = x_train, trControl = train_control, method = "lm", tol = 2e-16)

print(cvmodel)

summary(cvmodel)
```


```{r}
cvmodel$results
```

# Prediction
```{r}
predictions = predict(cvmodel, newdata = x_test, interval = "prediction")
```
```{r}

```

# Prediction Stats
```{r}
RMSE = sqrt(mean((predictions-y_test)^2))
RMSE
```

```{r}
#write.csv(x = data, 
#file = "C:\\Users\\Mark Anthony Carthon\\Documents\\NYCDSA\\Machine Learning Project Proposal\\Machine Learning Project Proposal\\_data")
```


```{r}

```


```{r}
python_data = data.frame(data$SalePrice, data$X1stFlrSF, data$X2ndFlrSF, data$Fireplaces,
                         data$TotalBsmtSF, data$ExterQual, data$HeatingQC, data$HalfBath,
                         data$BsmtQual, data$GarageArea, data$GarageFinish, data$YearRemodAdd,
                         data$KitchenQual, data$CentralAir, data$YearBuilt, data$isu_dist,
                         data$airport_dist, data$downtown_dist, data$Neighborhood)
```

```{r}
#python_data = sapply(python_data, as.numeric)
#python_data = as.data.frame(python_data)
```


```{r}
model = lm(data.SalePrice ~ ., data = python_data[,-19])
summary(model)
plot(model)
```









































































































































































































